Anomalous waves triggered by abrupt depth changes: laboratory experiments and truncated KdV statistical mechanics

### 2019-10-29 paper2_JNLS/paper.tex
NM

@@

% Figure
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[!ht]
\begin{center}
\includegraphics[width = 0.99 \linewidth]{Figs/slopehist.pdf}
\caption{
Comparison of slope histograms. The TKdV simulations show similar slope distributions upstream, but visual distributions in the downstream distributions are visible. While the simulations recover the spread of the downstream slope statistics, they do not capture the asymmetry seen in the experiments.
}
\label{slopehist}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

>>>>

\nick{ Also include machine-learning strategies \cite{MachineLearning2019}. }

@@

% Figure
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[!ht]
\begin{center}
\includegraphics[width = 0.99 \linewidth]{Figs/slopehist.pdf}
\caption{
Comparison of slope histograms. The TKdV simulations show similar slope distributions upstream, but visual distributions in the downstream distributions are visible. 
While the simulations recover the spread of the downstream slope statistics, they do not capture the asymmetry seen in the experiments \nick{to changes}.
}
\label{slopehist}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
